Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-07 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-front.tex
Version submitted 1

\begin{abstract}
The necessary intervention of humans in interactive evolutionary
computational systems has inherent drawbacks arising from the very nature of 
the algorithms, namely, the human fatigue caused by the interaction, and
the boredom arising when users evaluate a large number of artifacts.
To tackle these issues, in this paper we
propose a human-centered framework to model complex interactions on these systems.
Three case studies are presented where the model is applied in the 
development of evolutionary interactive systems, with different techniques:
volunteer-collaborative, unplugged and sensor-based. 
Both conceptual and implementation details are provided where the   
technique is applied to measure and increase user engagement and participation.
Our experiments show that the model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and boredom, and thus increase {\em performance} of the
interactive system.
\end{abstract}

>>>>

\begin{abstract}
The necessary intervention of humans in interactive evolutionary
computational systems has inherent drawbacks arising from the very nature of 
the algorithms, namely, the human fatigue caused by the interaction, and
the boredom arising when users evaluate a large number of artifacts.
To tackle these issues, in this paper we
propose a human-centered framework to model complex interactions on these systems.
A case study is presented where the model is applied in the 
development of a collaborative evolutionary interactive system. 
Both conceptual and implementation details are provided where the   
technique is used to measure and increase user engagement and participation.
Our experiments show that the model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and boredom, and thus increase the {\em performance} of the
interactive system.
\end{abstract}
